The Astropy Project

### 2017-11-28 main.tex

In order to check the accuracy of the coordinate transformations in \package{astropy.coordinates}, we have created a set of benchmarks that we use to compare transformations between a set of coordinate frames for a number of packages\footnote{\url{http://www.astropy.org/coordinates-benchmark/summary.html}}. Since
no package can be guaranteed to implement all transformations to arbitrary precision, and since some transformations are sometimes subject to interpretation of standards (in particular in the case of Galactic coordinates), we do not designate any of the existing packages as the `ground truth' but instead compare each tool to all other tools to find. The benchmarks are thus useful beyond the \astropy project since they allow all of the tools to be compared to all other tools. The tools included in the benchmark at the moment include the \astropypkg core package, Kapteyn \citep{kapteyn}, NOVAS \citep{novas}, PALpy \citep{pal}, PyAST \citep[a wrapper for AST, described in][]{ast}, PyTPM\footnote{\url{https://github.com/phn/pytpm}}, PyEphem \citep{pyephem}, and pySLALIB \citep[a Python wrapper for SLALIB, described in][]{slalib}.

>>>>

In order to check the accuracy of the coordinate transformations in \package{astropy.coordinates}, we have created a set of benchmarks that we use to compare transformations between a set of coordinate frames for a number of packages\footnote{\url{http://www.astropy.org/coordinates-benchmark/summary.html}}. Since
no package can be guaranteed to implement all transformations to arbitrary precision, and since some transformations are sometimes subject to interpretation of standards (in particular in the case of Galactic coordinates), we do not designate any of the existing packages as the `ground truth' but instead compare each tool to all other tools. The benchmarks are thus useful beyond the \astropy project since they allow all of the tools to be compared to all other tools. The tools included in the benchmark at the moment include the \astropypkg core package, Kapteyn \citep{kapteyn}, NOVAS \citep{novas}, PALpy \citep{pal}, PyAST \citep[a wrapper for AST, described in][]{ast}, PyTPM\footnote{\url{https://github.com/phn/pytpm}}, PyEphem \citep{pyephem}, and pySLALIB \citep[a Python wrapper for SLALIB, described in][]{slalib}.
